|

### 2020-11-25 Presentations/GenesAsEnviron.Rmd
AccFunc: use countour3 in evolDist to include several panels in a figure. Figure files: use several files to upload one scenario. Aga_figures: finished Improve cluster analysis cue_compt.cpp: Allow to insert types at the beggining of the simulations New simulation with different sd for the mutation kernel

---
title: | 
    | Learning can mediate the evolution of 
    | (cheap and costly) signals of quality
author: "Andrés Quiñones PhD."
bibliography: ../SocialMorphCue.bib
date: | 
    | 
    | 
    | Genes as environment - AGA2020 virtual symposium
    | `r format(Sys.time(), '%B %d, %Y')`
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
    \usepackage{xcolor}
---

@@

```{r,echo=FALSE,fig.align="center",out.width='40%',fig.show='hold'}

knitr::include_graphics("../Images/sexSelec.jpg")
knitr::include_graphics("../Images/begging.jpg")
knitr::include_graphics("../Images/broodparasite.jpg")
knitr::include_graphics("../Images/dominance.jpg")
```

@@

```{r,echo=FALSE,fig.align='center',out.height='80%'}
knitr::include_graphics("../Images//hosp_alexandra_mackenzie.jpg")

@@

## The handicap principle

### Badges of status

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("../Images//comSystemBot.png")
```

[@botero_Evolution_2010]

## Are bibs really badges?

```{r,echo=FALSE,fig.align='left',out.width='30%'}
knitr::include_graphics("../Images/Sanchez-Tojar_2018.png")
```

@@

\vspace{-0.5cm}

### Comunication

@@

```{r,echo=FALSE,fig.align='center',out.width='50%'}
 par(plt=posPlot(),las=1)
 rangeBeta<-c(4,10,-4,-10)
 rangQual<-seq(0,1,by = 0.01)
 linesSender<-sapply(rangeBeta,function(x)logist(rangQual,alpha = x/2,beta = x))
 plot(logist(rangQual,alpha = 0,beta = 0)~rangQual,type="l",xlab="Quality",
      ylab = expression(p[w]),cex.lab=2,lwd=2,col="grey",cex.axis=2,ylim=c(0,1))
 matlines(x=rangQual,y=linesSender,lwd=4,col=colRuns,lty=1)
 legend("left",legend=rangeBeta,col=colRuns,lwd=3,title = expression(beta),cex=2,bty="n")

@@

par(plt=posPlot(),las=1)
plot(logist(totRBF(rangx,centers,sigSq,weights),alpha = 0,beta=1)~rangx,type='l',col=1,
     xlab="",ylab="p(retreat)",ylim=c(0,1),lwd=3,xaxt="n",cex.lab=2,cex.axis=2)
points(y=logist(weights,alpha = 0,beta=1),x=centers,cex=3,pch=20)

@@

```{r,echo=FALSE,fig.align='center',out.width='60%'}
par(plt=posPlot(),las=1)
plot(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 2)~
       seq(-1,1,length.out = 1000),type="l",xlab="Difference in quality",
     ylab = expression(p[w]),cex.lab=2,lwd=3,col="red",cex.axis=2,ylim=c(0,1))
lines(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 10)~
       seq(-1,1,length.out = 1000),lwd=3,col="green")
legend("topleft",legend=c(2,10),col=c("red","green"),lwd=3,title = expression(beta),cex=2,bty="n")
```

@@

\pause
```{r, echo=FALSE,fig.align='center', out.width = '100%'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.6learnDyn.png")
```

<!-- ## Learning can mediate the evolution of Badges of Status -->
<!-- ### Variation among replicates -->
<!-- \small -->
<!-- set of simulations with the badge working as a handicap (cost inversely proportional to quality) -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='100%'} -->
<!-- knitr::include_graphics("../Simulations/betCostEvol1_/evolDynAll_betCost5.png") -->
<!-- ``` -->

@@

<!-- \small -->
<!-- One of the replicates of the previous slide, the badge as a handicap -->
```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn0_betCost5.png")
```

@@

```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn5_betCost5.png")
```

## Badges of Status: do they matter?
### Behavioural interactions

@@

```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/betCostEvol1_/compClustRep_betCost5.png")
```

@@

<!-- <!-- ### Variation among replicates --> -->
<!-- <!-- \small --> -->
<!-- <!-- Here simulations where the signal has no cost --> -->

@@

## The evolution of cheap Badges of Status

@@

```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/nIntGroupEvol4_/evolDyn13_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status

<!-- \tiny -->
<!-- Panels show the changes in frequency distribution along evolution ($\alpha$, $\beta$, and resulting badge respectively) for the replicate shown in the previous slide -->

<!-- Branching events in the reaction norm parameters yield three types of sender codes. One (more or less) -->
<!-- honest, two dishonest (one with a big badge and one with a small badge) -->

```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold', fig.cap="alpha - beta -Badge"}
knitr::include_graphics("../Simulations/nIntGroupEvol4_/evolDistAlpha13_nIntGroup2000.png")
knitr::include_graphics("../Simulations/nIntGroupEvol4_/evolDistBeta13_nIntGroup2000.png")
knitr::include_graphics("../Simulations/nIntGroupEvol4_/evolDistBadge13_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status
### How often does it happen?
<!-- \tiny -->
<!-- Values of $\alpha$ and $\beta$ for each individual in the different replicates. Each dot an individual, -->
<!-- each panel a replicate. Individuals are sampled from populations from the second half of the simulations. -->

@@

```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status
### Does it matter?
\small
Behavioural interactions splitting up the replicates according to the number of "types" that 
evolve

```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup2000.png")
```

<!-- ## Interaction structures - do they matter? -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='100%',} -->
<!-- knitr::include_graphics("../Images/networks.png") -->
<!-- ``` -->
<!-- [@chaine_Manipulating_2018] -->

<!-- ## Localized interaction structures -->

<!-- ### Costly signals  -->
<!-- \tiny -->
<!-- Behavioural interactions and badge size for simulations with costs where individuals interact in small groups. On the $x$ axes number of different individuals each focal interacts with. -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCost_/BehavIntALL.png") -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCost_/CueALL.png") -->
<!-- ``` -->

<!-- ## Localized interaction structures -->

<!-- ### Cheap signals (free) -->
<!-- \small -->
<!-- Variation among individuals in different replicates (just like before) in replicates where individuals interact with 10 other individuals. -->

<!-- A part from replicates with two clusters, the clustering seems less straightforward as before -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='85%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup10.png") -->
<!-- ``` -->

<!-- ## Localized interaction structures -->

<!-- ### Cheap signals (free)  -->

<!-- \small -->
<!-- Behavioural interactions for the replicates form previous slide. I split up the replicates according to clusters (despite clusters not being clear cut). -->

<!-- Only replicates with only one cluster seems to have less aggressive interactions -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup10.png") -->
<!-- ``` -->

<!-- ## Localized interaction structures -->

<!-- ### Cheap signals or Individual recognition? -->
<!-- \tiny -->
<!-- In these set, I changed the learning set up, I increased the number of centers (10 now, 6 before) -->
<!-- along the signal axis; and I reduced the level or generalization.  -->

<!-- There seems to be an effect on the slope of the reaction norm. It stays very close to zero.  -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCenters1_/evolDynALL_nIntGroup10.png") -->
<!-- ``` -->

<!-- ## Localized interaction structures -->

<!-- ### Cheap signals or Individual recognition -->
<!-- \small -->
<!-- Same replicates as the previous slide. Variation in $\beta$ and $\alpha$ among individuals for different replicates.  -->

<!-- No clear clustering. Variation mostly along the $\alpha$ axis -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCenters1_/corrAlphBet_nIntGroup10.png") -->
<!-- ``` -->
<!-- ## Localized interaction structures -->

<!-- ### Cheap signals or Individual recognition? -->
<!-- \small -->
<!-- Panels show the changes in frequency distribution along evolution ($\alpha$, $\beta$, and resulting badge respectively) for the replicate shown in the previous slide.  -->

<!-- $\beta$ around zero, $\alpha$ all over the place.  -->

<!-- ```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCenters1_/evolDistAlpha5_nIntGroup10.png") -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCenters1_/evolDistBeta5_nIntGroup10.png") -->
<!-- knitr::include_graphics("../Simulations/nIntGroupCenters1_/evolDistBadge5_nIntGroup10.png") -->
<!-- ``` -->

<!-- <!-- ## Aqui vamos! mirar correlaciones de 20 y 2000 luego interacciones --> -->

<!-- <!-- ## Comparar scenarios --> -->

@@

@@

\tiny
Here, I vary the aggressive tendency for unlearned individuals in these three set ups.

Agressive, peaceful, clever (starts at the ESS of the classic hawk-dove game)

```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'}
knitr::include_graphics("../Images/cartoonRBF_InitAct.png")
```

@@

### The peaceful

Variation among replicates

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/evolDynALL_initAct2.png")
```

@@

### The peaceful

Variation within one replicate

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/evolDyn2_initAct2.png")
```

### The peaceful

Changes in the frequency distributions

```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/evolDistAlpha2_initAct2.png")
knitr::include_graphics("../Simulations/initAct_/evolDistBeta2_initAct2.png")
knitr::include_graphics("../Simulations/initAct_/evolDistBadge2_initAct2.png")
```

### The peaceful

Favours variation and cheap signals

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/corrAlphBet_initAct2.png")
```

### The aggressive

Variation among replicates

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/evolDynALL_initAct-2.png")
```

### The aggressive

Variation within one replicate

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/evolDyn0_initAct-2.png")
```

### The aggressive

Disfavours variation and signal evolution - no signalling

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/corrAlphBet_initAct-2.png")
```

### The clever (ESS)

Variation among replicates

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/evolDynALL_initAct-0.69.png")
```

### The clever (ESS)

Variation within one replicate

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
  knitr::include_graphics("../Simulations/initAct_/evolDyn0_initAct-0.69.png")
```

### The clever (ESS)

Signal evolution seems to be driven by drift. Most replicates end up in one of the two extremes

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
  knitr::include_graphics("../Simulations/initAct_/corrAlphBet_initAct-0.69.png")
```

@@

### Costly signals
- Learning can mediate costly signals
- More expensive signals seem be more likely to evolve
- Less expensive signals provide more information
- Local interactions do not impede the evolution of costly signals (as has been suggested)

### Cheap signals
- Learning mediates the evolution of polymorphisms with "honest" and "dishonest"
individuals
- Under local interactions learning seems to allow the evolution of IR
- Cheap signals depend on the innate level of aggression (before learning) of individuals
- Peace begets heterogeneity, aggression begets homogeneity

>>>>

---
title: | 
    | Learning can mediate the evolution of 
    | (cheap and costly) signals of quality
author: "Andrés Quiñones PhD."
bibliography: ../SocialMorphCue.bib
date: | 
    | 
    | 
    | Genes as environment - AGA2020 virtual symposium
    | November 17 - 2020
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
    \usepackage{xcolor}
---

## Acknowledgements

| ![Red1](../Images/redouan.jpg){width=33%} | ![Olle](../Images/olof-leimar.png){width=23%} | ![Daniel](../Images/danielcadena.jpg){width=32%}  |
| :---:        |    :----:   |    :---: |
| *R. Bshary* |*O. Leimar*|*D. Cadena*|

![unine](../Images/UNINE_cmjn.jpg){width=35%}
![uniandes](../Images/logo_largo.png){width=45%}

@@

```{r,echo=FALSE,fig.align="center",out.width='40%'}

knitr::include_graphics("../Images/sexSelec.jpg")
knitr::include_graphics("../Images/dominance.jpg")
```

@@

```{r,echo=FALSE,fig.align='center',out.width='45%',fig.show='hold'}
knitr::include_graphics("../Images/HouseSparrow_strong.jpg")
knitr::include_graphics("../Images/HouseSparrow_weak.jpg")
```

@@

<!-- ## The handicap principle -->

<!-- ### Badges of status -->

<!-- ```{r,echo=FALSE,fig.align='center',out.width='90%'} -->
<!-- knitr::include_graphics("../Images//comSystemBot.png") -->
<!-- ``` -->

<!-- [@botero_Evolution_2010] -->

<!-- ## Are bibs really badges? -->

<!-- ```{r,echo=FALSE,fig.align='left',out.width='30%'} -->
<!-- knitr::include_graphics("../Images/Sanchez-Tojar_2018.png") -->
<!-- ``` -->

<!-- [@sanchez-tojar_Metaanalysis_2018a] -->

@@

\vspace{-0.3cm}

```{r,echo=FALSE,fig.align='center',out.width='60%'}
par(plt=posPlot(),las=1)
plot(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 2)~
       seq(-1,1,length.out = 1000),type="l",xlab="",
     ylab = expression(p[w]),cex.lab=3,lwd=3,col="red",cex.axis=2,ylim=c(0,1))
 mtext("Difference in quality",1,line = 4,cex = 3,las = 0)
lines(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 10)~
       seq(-1,1,length.out = 1000),lwd=3,col="springgreen4")
legend("topleft",legend=c(2,10),col=c("red","springgreen4"),lwd=3,title = expression(beta),cex=2,bty="n")
```

### Communication

@@

```{r,echo=FALSE,fig.align='center',out.width='50%'}
 par(plt=posPlot(),las=1)
 rangeBeta<-c(4,10,-4,-10)
 rangQual<-seq(0,1,by = 0.01)
 linesSender<-sapply(rangeBeta,function(x)logist(rangQual,alpha = x/2,beta = x))
 plot(logist(rangQual,alpha = 0,beta = 0)~rangQual,type="l",xlab="",
      ylab ="",cex.lab=2,lwd=2,col="grey",cex.axis=2,ylim=c(0,1))
 mtext("Quality",1,line = 4,cex = 3,las = 0)
 matlines(x=rangQual,y=linesSender,lwd=4,col=colRuns,lty=1)
 mtext("Badge size",2,line = 4,cex = 3,las = 0)
 legend("left",legend=rangeBeta,col=colRuns,lwd=3,title = expression(beta),cex=2,bty="n")

@@

par(plt=posPlot(),las=1)
plot(logist(totRBF(rangx,centers,sigSq,weights),alpha = 0,beta=1)~rangx,type='l',col=1,
     xlab="",ylab="",ylim=c(0,1),lwd=3,xaxt="s",cex.lab=2,cex.axis=2)
# test<-sapply(1:6, function(x){RBF()})
points(y=logist(weights,alpha = 0,beta=1),x=centers,cex=3,pch=20)
# xRBFs<-sapply(centers, function(x){seq(x-0.2,x+0.2,by=0.001)})
# RBFS<-sapply(1:6, function(x){
#   logist(weights[x]*RBF(seq(centers[x]-0.2,centers[x]+0.2,by=0.001),xCenter = centers[x],
#                         sigSq = 0.01))
# })
# matlines(x=xRBFs,y=RBFS,col="grey",lty=2,lwd=2)

mtext("p(dove)",2,line = 4,cex = 3,las = 0)
mtext("Badge size",1,line = 4,cex = 3,las = 0)

@@

@@

```{r, echo=FALSE,fig.align='center', out.width = '100%'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.4learnDyn.png")
```

@@

<!-- \small -->
<!-- One of the replicates of the previous slide, the badge as a handicap -->
```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn0_betCost5.png")
```

@@

```{r, echo=FALSE,fig.align='center', out.height='90%'}
knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn5_betCost5.png")
```

<!-- ## Badges of Status: do they matter? -->
<!-- ### Behavioural interactions -->

@@

<!-- ```{r, echo=FALSE,fig.align='center', out.width='90%'} -->
<!-- knitr::include_graphics("../Simulations/betCostEvol1_/compClustRep_betCost5.png") -->
<!-- ``` -->

@@

<!-- <!-- ### Variation among replicates --> 
<!-- <!-- \small --> 
<!-- <!-- Here simulations where the signal has no cost -->

@@

## The evolution of cheap badges of Status

@@

```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000.png")
```

<!-- ## The evolution of cheap Badges of Status -->
<!-- ### How often does it happen? -->
<!-- \tiny -->
<!-- Values of $\alpha$ and $\beta$ for each individual in the different replicates. Each dot an individual, -->
<!-- each panel a replicate. Individuals are sampled from populations from the second half of the simulations. -->

@@

<!-- ```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupNormQual_/corrAlphBet_nIntGroup2000.png") -->
<!-- ``` -->

<!-- ## The evolution of cheap Badges of Status -->
<!-- ### Does it matter? -->
<!-- \small -->
<!-- Behavioural interactions splitting up the replicates according to the number of "types" that  -->
<!-- evolve -->

<!-- ```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup2000.png") -->
<!-- ``` -->

@@

\vspace{-1cm}

@@

<!-- \tiny -->
<!-- Here, I vary the aggressive tendency for unlearned individuals in these three set ups. -->

<!-- Agressive, peaceful, clever (starts at the ESS of the classic hawk-dove game) -->

```{r,out.width='45%',fig.show='hold'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.4learnDyn.png")
# knitr::include_graphics("../Images/cartoonRBF_InitAct.png")
nCenters<-6
interv<-1/(nCenters-1)
centers<-interv*seq(0,nCenters-1)
sigSq<-0.01
weights<-data.table(neutral=rep(0,nCenters),agressive=rep(-2,nCenters),
        peaceful=rep(2,nCenters),clever=rep(-0.69,nCenters))
rangx<-seq(0,1,length=1000)

par(plt=posPlot(numploty = 2,idploty = 2),las=1)
actor<-sapply(weights, Actor,centers=centers)

par(plt=posPlot()*0.95)
matplot(x=rangx,y=as.matrix(actor),type='l',col=c("black","red","blue","springgreen4"),lty=1,
     xlab="",ylab="",ylim=c(0,1.1),lwd=5,xaxt="s",cex.lab=1.5,cex.axis=2)
mtext(text = "p(dove)",2,line = 4,cex = 2.5,las=0)
mtext(text = "Badge size",1,line = 3.5,cex = 2.5)
points(y=logist(weights$neutral,alpha = 0,beta=1),x=centers,cex=3)
text(y = actor[1,]+0.1,x=rep(0.5,4),col=c("black","red","blue","springgreen4"),
     labels = names(weights),cex=2)
```

@@

```{r,echo=FALSE,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter_1.png")

@@

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter_.png")

@@

### Costly signals
- Learning can mediate costly signals

### Cheap signals
- Learning mediates the evolution of polymorphisms with "honest" and "dishonest"
individuals
- Cheap signals depend on the innate level of aggression (before learning) of individuals
